Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-02 sections/correlated-sicm-and-fm.tex
changed $-$ to --

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate, sowohl %german
the cell membrane with a technique, which is able to do so $–$ AFM \cite{}, EM \cite{}, SICM 
\cite{Hansma1989} $-$, als auch %german
to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

@@

Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
simultaneously and $-$ because fluorescence signals should be investigated, which were originated
from particles at or near to the surface of the cell $-$ it was important to keep the distance 
between the sample and the pipette constant. In that study the SSCM was used for investigating the 
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.

@@

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors 
\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
After measuring the topography (SICM) the nanopipette could be moved to places $-$ e.g. the 
z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} $-$ where the 
adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
conformation and a FRET signal could be detected \cite{Nikolaev2010}.

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate, sowohl %german
the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
\cite{Hansma1989} --, als auch %german
to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

@@

Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
simultaneously and -- because fluorescence signals should be investigated, which were originated
from particles at or near to the surface of the cell -- it was important to keep the distance 
between the sample and the pipette constant. In that study the SSCM was used for investigating the 
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.

@@

SICM in combination with F\"orster resonance energy transfer (FRET) sensors could be used for
the localisation of {$\beta_{1}$}-adrenoceptors \cite{Wright2018}, {$\beta_{2}$}-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and {$\beta_{3}$-adrenoceptors 
\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
conformation and a FRET signal could be detected \cite{Nikolaev2010}.
